Articles_Plots

### 2023-02-10 r1_Articles.Rmd
rmarkdown files updated after adding MSE for MLE

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Accuracy",
                                        All_ACC))

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# OSMAC
load(here("Identical_r0","Summary","Classical","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# Colors_mVc<-Colors_mVc<-c("#88CCEE",#"#A6C3D3","#5D92B0","#35586C", 
#                           "#FFC4D8","#E28490","#BB2C3E","#55141C", 
#                           "#DDCC77")

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+#
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Accuracy of Y")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(paste0(expression(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Accuracy of Y")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6

@@

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "r1_SMSE_MI_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "r1_SMSE_MI_LR_TV_Exp_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_LR_TV_Exp_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
```

>>>>

# OSMAC
load(here("Identical_r0","Summary","Model_1","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# All elements
All_MSE<-rbind(OSMAC_MSE[,!(colnames(OSMAC_MSE) %in% "Type")])
All_MSE_MLE<-rbind(OSMAC_MSE_MLE[,!(colnames(OSMAC_MSE_MLE) %in% "Type")])
All_Info<-rbind(OSMAC_Info[,!(colnames(OSMAC_Info) %in% "Type")])
All_ACC<-rbind(OSMAC_ACC[,!(colnames(OSMAC_ACC) %in% "Type")])

@@

colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_MSE_MLE)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

M1_Identical_r0<-rbind(cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Model Information",
                                        All_Info),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE",
                                        All_MSE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="MSE for MLE",
                                        All_MSE_MLE),
                       cbind.data.frame(Covariate="Data Model: x\u2081, x\u2082",Metric="Accuracy",
                                        All_ACC))

remove(All_Info,All_MSE,RS_Info,RS_MSE,All_ACC)
```

@@

# OSMAC
load(here("Identical_r0","Summary","Model_2","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# OSMAC
load(here("Identical_r0","Summary","Model_3","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# OSMAC
load(here("Identical_r0","Summary","Model_4","Data","Efficiency","No_Correlated_Covariate_OSMAC_r1.RData"))
remove_stuff<-c(paste0("Assumed New ",1:3))
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_MSE_MLE<-All_MSE_MLE[!(All_MSE_MLE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_ACC<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

# Colors_mVc<-Colors_mVc<-c("#FFC4D8","#E28490","#BB2C3E","#55141C", 
#                           "#DDCC77")

@@

#Identical_ro<-Identical_ro[Identical_ro$Subsample_Size %in% seq(100,1000,100),]

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mMSE

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 4)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Average Model Information")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+guides(colour = guide_legend(nrow = 2))+Theme_special()->Temp_plot_mVc

@@

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p1

Identical_ro[Identical_ro$Metric=="Model Information" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(Average Model Information)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p2

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p3

Identical_ro[Identical_ro$Metric=="MSE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p4

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Accuracy of Y")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p5

Identical_ro[Identical_ro$Metric=="Accuracy" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("Accuracy of Y")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p6

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mMSE,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p7

Identical_ro[Identical_ro$Metric=="MSE for MLE" & Identical_ro$Model %in% Selected_Models_mVc,] %>%
  ggplot(.,aes(x=Subsample_Size,y=log(`Estimated Values`),color=Model))+
  scale_x_continuous(labels = unique(Identical_ro$Subsample_Size),
                     breaks = unique(Identical_ro$Subsample_Size))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mVc)+
  facet_wrap(~Covariate,scales = "free_y",ncol = 2)+
  xlab(expression(paste(r[0],' + ',r[1],'=1000 and ',r[0])))+
  ylab("log(SMSE)")+
  scale_y_continuous(breaks = scales::pretty_breaks(n = length(unique(Identical_ro$Subsample_Size))/2))+
  theme_bw()+Theme_special()->p8

@@

ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom")
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom")

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>%
  ggexport(filename = "r1_SMSE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_ACCURACY_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 12)
ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_LR_TV_Exp_mMSE.pdf",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_LR_TV_Exp_mVc.pdf",res=300,width = 12,height = 12)

ggarrange(p1,p3,nrow = 2,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom",labels = "auto") %>%
  ggsave(filename = "r1_SMSE_MI_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p2,p4,nrow = 2,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom",labels = "auto") %>% 
  ggsave(filename = "r1_SMSE_MI_LR_TV_Exp_mVc.eps",device="eps",dpi=300,width = 12,height = 16)
ggarrange(p5,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_LR_TV_Exp_mMSE.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p6,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggsave(filename = "r1_ACCURACY_LR_TV_Exp_mVc.eps",device="eps",dpi=300,width = 12,height = 12)
ggarrange(p7,nrow = 1,ncol = 1,legend.grob = Temp_legend_mMSE,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_LR_TV_Exp_mMSE.eps",res=300,width = 12,height = 12)
ggarrange(p8,nrow = 1,ncol = 1,legend.grob = Temp_legend_mVc,legend = "bottom") %>%
  ggexport(filename = "r1_SMSE_for_MLE_MI_LR_TV_Exp_mVc.eps",res=300,width = 12,height = 12)
```
